\documentclass{muratcan_cv}

\setname{H Harinadh}{}
\setaddress{Your Address}
\setmobile{+91 7842845297}
\setmail{harinadhcbse@gmail.com}
\setlinkedinaccount{https://www.linkedin.com/in/h-harinadh/} 
\setgithubaccount{https://github.com/Eccentric-Harry}
\settwitteraccount{https://x.com/h_harinadh_}
\setleetcodeaccount{https://leetcode.com/u/harinathrao13/}
\setthemecolor{MidnightBlue}

\begin{document}

% Create header
\headerview
\vspace{1ex} % white space

\section{Education} 
    \datedexperience{Bachelor of Technology in Computer Science and Engineering}{Oct 2022 -- Present}
    \explanation{Vellore Institute of Technology – AP University}{CGPA: 9.11} 
    \datedexperience{Secondary and Higher Secondary Education}{June 2014 -- May 2021}
    \explanation{Sainik School Korukonda}{Percentage: 91\%}

\section{Skills}
    \newcommand{\skillone}{\createskill{Languages}{Java \cpshalf Python \cpshalf JavaScript \cpshalf HTML \cpshalf CSS}}
    \newcommand{\skilltwo}{\createskill{Frameworks}{MongoDB \cpshalf ExpressJS \cpshalf ReactJS \cpshalf NodeJS}}
    \newcommand{\skillthree}{\createskill{Tools}{Git \cpshalf GitHub \cpshalf React-Query \cpshalf React Hook Form \cpshalf React Toast \cpshalf Appwrite \cpshalf Cloudinary \cpshalf Vercel \cpshalf Render}}
    \newcommand{\skillfour}{\createskill{Concepts}{Data Structures \& Algorithms \cpshalf Object-Oriented Programming \cpshalf Computer Networks \cpshalf DBMS \cpshalf OS}}
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour}
    \vspace{-3mm} % reduces whitespace!

\section{Experience}
    \datedexperience{Community Manager}{April 2024 -- Present}
    \explanation{Microsoft Student Chapter, VIT-AP University}{}
    \explanationdetail{
    \smallskip
    \coloredbullet\ %
    Lead the Tech teams and focused on posting innovative tech updates and coding reels on social media.
    
    \smallskip 
    \coloredbullet\ %
    Engaged over 1000+ users with informative tech reels and updates.
     
    \smallskip
    \coloredbullet\ %
    Managed content creation to explain important and trending coding concepts.
    
    \smallskip
    \coloredbullet\ %
    Coordinated with team members to ensure timely and impactful content delivery.
    \smallskip
    }

\section{Notable Projects}
    \datedexperience{Streamify Web Application \href{https://videotube-rust.vercel.app/}{[Link]}}{May 2024 -- July 2024}
    \explanation{Full-Stack Developer}{MERN, Cloudinary, TanStack/React-Query, React Toast} 
    \explanationdetail{
    \smallskip
    \coloredbullet\ %
    Developed a full-featured web platform enabling video uploads, user authentication, and video playback.
     
    \smallskip
    \coloredbullet\ %
    Engineered the application using the MERN stack for a robust and scalable environment.
     
    \smallskip
    \coloredbullet\ %
    Deployed the frontend on Vercel and the backend on Render, ensuring seamless CI/CD processes.
     
    \smallskip
    \coloredbullet\ %
    Integrated Cloudinary for efficient video file storage and management.
     
    \smallskip
    \coloredbullet\ %
    Leveraged TanStack/React-Query for optimized data fetching, enhancing app performance.
     
    \smallskip
    \coloredbullet\ %
    Implemented user-friendly forms with React Hook Form to streamline interactions.
    \smallskip
    }
    
    \datedexperience{Blogging Web Application (Blogs) \href{https://appwrite-blog-two-opal.vercel.app/}{[Link]}}{April 2024 -- May 2024}
    \explanation{Full-Stack Developer}{Vite, React, Redux, React Hook Form, TinyMCE, Vercel}
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
    Created a dynamic blogging platform featuring user authentication, post creation, and rich text editing.
     
    \smallskip
    \coloredbullet\ %
    Utilized Vite and React for a highly responsive development experience.
     
    \smallskip
    \coloredbullet\ %
    Managed global state with Redux and form handling with React Hook Form for better performance.
     
    \smallskip
    \coloredbullet\ %
    Configured intuitive navigation using React Router.
     
    \smallskip
    \coloredbullet\ %
    Successfully deployed on Vercel, ensuring continuous integration and delivery.
    \smallskip
    }
    
    \datedexperience{Mental Health Web Application (Hackathon) \href{https://better-care-tau.vercel.app/}{[Link]}}{Feb 2024}
    \explanation{Lead Frontend Developer}{Vite, React, Tailwind CSS, React-Router DOM}
    \explanationdetail{
    \smallskip
    \coloredbullet\ %
    Led the frontend development for a mental health support platform, coordinating with the backend team.
     
    \smallskip
    \coloredbullet\ %
    Successfully integrated frontend with backend, setting up essential API endpoints.
     
    \smallskip
    \coloredbullet\ %
    Designed a comprehensive user interface for mental health resources and user profiles.
     
    \smallskip
    \coloredbullet\ %
    Utilized Vite for fast prototyping and React for modular, component-based architecture.
     
    \smallskip
    \coloredbullet\ %
    Applied Tailwind CSS and Designed the website for a modern, responsive UI.
    \smallskip
    }

\section{Achievements and Certifications}
\indent
\explanationdetail{
\smallskip
\coloredbullet\ %
\textbf{PCAP Programming Essentials in Python} Certified by Cisco Networking Academy
    
\smallskip 
\coloredbullet\ %
\textbf{AWS Cloud Practitioner Certification} (Currently Undergoing)
     
\smallskip
\coloredbullet\ %
\textbf{Ranked 26th} out of 100 teams in `CODE STORM` national event organized by SCOPE, NextGen Cloud club, and Microsoft Student Chapter
     
\smallskip
\coloredbullet\ %
\textbf{Ranked 5th} in National Wide Hackathon “HackFest2k24” Organized by CSI Chapter
     
\smallskip
\coloredbullet\ %
\textbf{Solved} Over 150+ DSA Problems on Leetcode, GeeksForGeeks, InterviewBit
\smallskip

\coloredbullet\ %
\textbf{JavaScript Essentials Certification} from Cisco Networking Academy
\smallskip
}

\section{Soft Skills}
\indent
\explanationdetail{
\smallskip
\textbf{Excellent Communication, Teamwork, and Problem-solving skills} demonstrated through various team projects and leadership roles. {Disciplined and punctual, with a strong ability to adapt to new challenges and deliver results efficiently.}
\smallskip
}


\end{document}
